Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-02-09 paper/zhang-cook-laa-langrene-menendez.Rmd
tour path on torus

>>>>

```{r toy-torus, fig.cap="Six frames selected from animating 5000 randomly generated 2D projection bases. \\textcolor{red}{one more sentence here.} The full video of the animation can be found at \\url{https://vimeo.com/user133215810/review/510046144/49e902d8ef}. "}
```

The orthogonality of the axes in the basis corresponds to the two circles being perpendicular to each other in the torus.

### 2021-02-09 paper/zhang-cook-laa-langrene-menendez.tex
tour path on torus

>>>>

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-torus-1}

\caption{Six frames selected from animating 5000 randomly generated 2D projection bases. \textcolor{red}{one more sentence here.} The full video of the animation can be found at \url{https://vimeo.com/user133215810/review/510046144/49e902d8ef}. }\label{fig:toy-torus}
\end{figure}
\end{Schunk}

The orthogonality of the axes in the basis corresponds to the two
circles being perpendicular to each other in the torus.
